\documentclass[10pt,letterpaper]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage[english]{babel}
\hyphenation{Some-long-word}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}

\usepackage{resume}

\begin{document}

\begin{center}
	\textbf{\LARGE Archit Pandey}\\[1ex]
	\textscale{1.063}{
		\faInbox\hspace{0.5ex}\href{mailto:architpa@usc.edu}{architpa@usc.edu}
		% \href{mailto:archpndy@gmail.com}{archpndy@gmail.com}
		\hspace{1ex}
		\faLinkedin\hspace{0.5ex}\href{https://linkedin.com/in/archit-p}{linkedin.com/in/archit-p}
		\hspace{1ex}
		\faGithub\hspace{0.5ex}\href{https://github.com/archit-p}{github.com/archit-p}
		\hspace{1ex}
		\faMobilePhone\hspace{0.5ex} +91 97423 55213
	}
\end{center}

% \vspace{-0.5ex}

\roottitle{Education}

\headedsectionfive
{University of Southern California}
{Los Angeles, CA}
{MS in Computer Science}
{Starting Aug 2021}

\headedsectionfive
{National Institute of Technology Karnataka}
{Surathkal, India}
{BTech in Computer Science and Engineering, GPA 9.05}
{Aug 2016 -- May 2020}

\roottitle{Languages and Technologies}
\begin{circlist}
	\item Javascript, Java, Go, Python, C, C++
	\item Node.js, React, Spring Boot, Docker, Kafka, PostgresQL, MongoDB, Redis, OpenNetVM, DPDK
\end{circlist}

\roottitle{Work Experience}
\headedsection
{Deskera}
{Pune, India}
{Software Development Engineer 1}
{Aug 2020 -- Present}{
	\begin{circlist}
		\item Built the Deskera ECom app (\textit{React}) and microservices (\textit{Spring Boot}) to manage e-commerce stores.
		\item Implemented long-running data synchronization jobs using Redis Lists as a job queue. This resulted in reduced data loss and faster recovery for running jobs in case of a service failure.
		\item Used Debezium for change capture and Kafka for passing events between services, leading to a 2x speedup in web service response time versus an inter-service call based approach.
	\end{circlist}
}

\headedsection
{University of Ottawa}
{Ottawa, Canada}
{Visiting Student Researcher under Prof. David Knox}
{May 2019 -- Aug 2019}{
	\begin{circlist}
		\item Built an intrusion detection technique that profiles malware using text-mining of network traffic.
		\item The technique encodes packets into words and packet flows into \textit{n-grams}. These \textit{n-grams} are vectorized using Doc2Vec, and fed into a Support Vector Machine (SVM) classification model.
		\item When evaluated against the DeepTraffic network traffic dataset (flow length being varied), our model obtained a 0.95 precision, 0.94 accuracy and 0.89 F1 score in malware classification.
	\end{circlist}
}

\headedsection
{Indian Institute of Science}
{Bangalore, India}
{Research Intern under Prof. K. Gopinath}
{May 2018 -- Jul 2018}{
	\begin{circlist}
		\item Studied performance of various Bitcoin nodes - payment verification nodes, full nodes with and without pruning.
		\item Implemented a compression algorithm to reduce size of Bitcoin blocks and the blockchain, using history summarization and LZ77 compression, resulting in a 0.78 compression ratio.
	\end{circlist}
}

\roottitle{Selected Projects}

\headedsectiontwo
{Handwritten Equation Solver}{}{}
{
	% [\href{https://github.com/Handwritten-Equation-Solver/Handwritten-Equation-Solver}{Code}]
	Android application that solves math equations in an image, using connected-component based image segmentation and a CNN model (\textit{Keras}) for symbol recognition. \textit{Node.js, Tensorflow}.
}

\headedsectiontwo
{React Database}{}{}
{
	Database-like web component with support for data types, sorting and filtering. \textit{React}.
}

\headedsectiontwo
{DPDK Framework for Queue Management}{}{}
{
	% [\href{https://ieeexplore.ieee.org/document/9289914}{Pub}]
	High-performance (tested upto 40Gbps bandwidth), lightweight (1000 lines of C) framework for managing congestion in queues (ex. cloud service queues). \textit{DPDK, C}.
}

\headedsectiontwo
{ONVM-Snort}{}{}
{
	% [\href{https://github.com/sdnfv/onvm-snort}{Code}]
	Virtualized Network Function (VNF) for the Snort IDS. \textit{C, OpenNetVM}.
}

\headedsectiontwo
{VoteChain}{}{}
{
	% [\href{https://github.com/archit-p/votechain}{Code}]
	% [\href{https://ieeexplore.ieee.org/document/8978295}{Pub}]
	Distributed voting system using blockchain as a ledger to store votes. \textit{Python}.
}

\headedsectiontwo
{Secure Biometric Authentication System}{}{}
{
	% [\href{https://github.com/archit-p/privacy-preserving-biometrics}{Code}]
	Application to authenticate a user using encrypted bio-metric data. \textit{C++}.
}

\roottitle{Awards and Additional Experience}

\begin{circlist}
	\item \textbf{Mitacs Globalink Grant 2019}\hspace{0.5em}One of 1500 selected globally out of 100,000+ applicants.
	\item \textbf{Narendra Summer Fellowship 2018}\hspace{0.5em}One of 13 selected in India out of 2,000+ applicants.
	\item \textbf{Chair at IEEE NITK}\hspace{0.5em}Led 150 volunteers in organizing programming workshops and mentoring events.
\end{circlist}

% \spacedhrule{0.8ex}{0.0ex}
% \roottitle{Extra-Curricular Activities}
% \headedsectiontwo
% {Chair at IEEE NITK}{}{}
% {\vspace{-2.4ex}
%     \begin{circlist}
%         \item Managed \textit{Envision}, a program to mentor freshmen on yearlong projects, seeing 100+ participants \& 15+ successful projects.
%         \item Organized 4 workshops across colleges in the Dakshina Kannada region on topics such as Git, Image Processing, etc.
%     \end{circlist}
% }

\end{document}
